### 2025-12-05 disser/part2.tex
fz

In this section, we perform axisymmetric MHD modeling of the W50 nebula around the microquasar SS 433. It has a characteristic shape: a central spherical part and two opposite lobes to the east and west of the central source. The X-ray emission of the nebula is very inhomogeneous, with several bright X-ray regions - `e1", `e2", and `e3' to the east and `w1' and `w2' to the west \cite{Safi-Harb1997}. Following \cite{Churazov}, we model a wind from the central microquasar with two components - quasi-isotropic slow wind and a more collimated outflow, the polar wind. The kinetic power of each component is about $10^{39}$ erg/s, and the velocities are $\approx3000$ km/s for the isotropic wind and $\approx0.2~c$ for the jet. Interactions of the collimated outflow, isotropic wind, and ambient medium cause several recollimation shocks in the jet, which explains the existence of different X-ray emitting regions. The sketch of the hydrodynamical model with the emission regions shown from \cite{Safi-Harb2022, IXPE2024SS433} is presented in Figure \ref{Scheme}.

>>>>

Туманность W50 имеет специфическую форму - у нее есть сферическая центральная часть и две вытянутые структуры к востоку и западу от ентрального источника. Рентгеновское излучение туманности неоднородно, а происходит от нескольких ярких областей - `e1", `e2", и `e3' на восточной стороне, `w1' и `w2' на западной \cite{Safi-Harb1997}. Следуя работе \cite{Churazov}, мы инициализируем течение из микроквазара в виде двух компонент - квазисферический медленный ветер и направленный транс-релятивистский полярный ветер (джет). Кинетическая мощность каждой компоненты составляет $2\times10^{39}$ erg/s, скорость медленного ветра - $\approx3000$ km/s, скорость полярного ветра $\approx0.2~c$. В результате взаимодействия направленного ветра, изотроного ветра и межзвездной среды образуются реколлимационные ударные волны в направленном ветре, что позволяет объяснить наличие нескольких ярких рентгеновских областей. Схема гидродинамической модели с излучающими областями, использованными в работах  \cite{Safi-Harb2022, IXPE2024SS433} показана на рисунке \ref{Scheme}.
